Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Don't repeat what's already said in the introduction

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain. Since
Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
of domains, domains have shifted to those probabilistically interesting
domains, which are difficult for replanners. Often domains that don't pass
this test are deemed to be classical planners in disguise, favoring the use of
replanners.

>>>>

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain.
